Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-07 doc/manuscript/manuscript.Rmd
Create broad category; move agressiveness
add initial sentence for Genotype community analysis

### Aggressiveness Assessment {-}

@@

@@

To assess the connectivity of shared genotypes across populations, we first tabulated the multilocus genotypes shared between at least two populations (defined as states or countries) with the *poppr* function `mlg.crosspop()` [@kamvar2014poppr].
From these data, we were able to construct a graph with populations as nodes and shared genotypes as edges (connections) between the nodes using the R packages *igraph* version 1.0.1 [@csardi2006igraph], *dplyr* version 0.7.1 [@dplyr], and *purrr* version 0.2.2.2 [@purrr].
Each node was weighted by the fraction of shared MLGs.
Each edge represents a single MLG, but because a single MLG could cross populations, that MLG may be represented by (n\*(n-1))/2 edges where n represents the number of populations it crosses.
Edges were weighted by $1-P_{sex}$, where $P_{sex}$ is the probability of encountering the same genotype via two independent meiotic events [@arnaud2007standardizing, @parks1993study].
We then used the `cluster_optimal()` function from *igraph* to define communities [@csardi2006igraph].
The graph was plotted using the R packages *ggplot2* version 2.2.1 [@ggplot2] and *ggraph* version 1.0.0 [@ggraph].
To ensure that we were able to capture the same community signal, we additionally ran this analysis including the 5 polymorphic markers described above.

>>>>

## Assessing importance of categorical and phenotypic variables  {-}

@@

### Aggressiveness assessment {-}

@@

As many disparate geographic regions shared multilocus genotypes, we wanted to know if we could find any patterns in connectivity. 
To assess the connectivity of shared genotypes across regions, we first tabulated the multilocus genotypes shared between at least two populations (defined as states or countries) with the *poppr* function `mlg.crosspop()` [@kamvar2014poppr].
From these data, we were able to construct a graph with populations as nodes and shared genotypes as edges (connections) between the nodes using the R packages *igraph* version 1.0.1 [@csardi2006igraph], *dplyr* version 0.7.1 [@dplyr], and *purrr* version 0.2.2.2 [@purrr].
Each node was weighted by the fraction of shared MLGs.
Each edge represents a single MLG, but because a single MLG could cross populations, that MLG may be represented by (n\*(n-1))/2 edges where n represents the number of populations it crosses.
Edges were weighted by $1-P_{sex}$, where $P_{sex}$ is the probability of encountering the same genotype via two independent meiotic events [@arnaud2007standardizing, @parks1993study].
We then used the `cluster_optimal()` function from *igraph* to define communities [@csardi2006igraph].
The graph was plotted using the R packages *ggplot2* version 2.2.1 [@ggplot2] and *ggraph* version 1.0.0 [@ggraph].
To ensure that we were able to capture the same community signal, we additionally ran this analysis including the 5 polymorphic markers described above.
